R Notebook

### 2016-06-28 TPR_FPR.rmd
save TPR before changes

library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library('ggplot2')
library('gbm')
library('randomForest')
library('caret')
library('pROC')
library('testthat')
library('purrr')
library(tidyr)
library('broom')
library('stringr')

@@

```{r}
if(.Platform$OS.type == 'windows'){
best.fin<- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/best_fin.rds")
plot.fin <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance_100_3.rds")
} else{
best.fin<- readRDS("~/Documents/github/consult/finalwriteup/report_data/best_fin.rds")
plot.fin <- readRDS("~/Documents/github/consult/finalwriteup/report_data/plot_finance_100_3.rds")
}

@@

} else{
CR.av_simplog<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_av_simplog.rds")
CR.comprf<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_comprf.rds")
CR.FWLS<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_FWLS.rds")
CR.simpboost<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_simpboost.rds")
CR.compboost<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_FWLScomp_boost.rds")
joined <- readRDS("/Users/yam/Documents/github/consult/finalwriteup/report_data/joined.rds")

@@

saveRDS(conf.plot, "~/Documents/github/consult/finalwriteup/report_data/conf_plot.rds")

@@

#iOS
all6 <- all6 %>% select(mlsto, balance.mlsto) %>% distinct()
all6$mlsto <- as.character(all6$mlsto)
df.blend = left_join(df.blend, all6)

#merge simp.log
head(new.CR)
all10mice<- cbind(all10mice, new.CR %>% select(simp.log))

>>>>

library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library('ggplot2')
library('gbm')
library('randomForest')
library('caret')
library('pROC')
library('testthat')
library('purrr')
library(tidyr)
library('broom')
library('stringr')
library('knitr')

@@

```{r}
if(.Platform$OS.type == 'windows'){
best.fin<- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/best_fin.rds")
plot.fin <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance_100_4.rds")
} else{
best.fin<- readRDS("~/Documents/github/consult/finalwriteup/report_data/best_fin.rds")
plot.fin <- readRDS("~/Documents/github/consult/finalwriteup/report_data/plot_finance_100_4.rds")
}

@@

} else{
CR.av_simplog<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_av_simplog.rds")
CR.comprf<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_comprf.rds")
CR.FWLS<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_FWLS.rds")
CR.simpboost<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_simpboost.rds")
CR.compboost<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results_FWLScomp_boost.rds")
# CR<- readRDS("~/Documents/github/consult/finalwriteup/report_data/finance_results.rds")
joined <- readRDS("/Users/yam/Documents/github/consult/finalwriteup/report_data/joined.rds")

@@

# saveRDS(conf.plot, "~/Documents/github/consult/finalwriteup/report_data/conf_plot.rds")

@@

#iOS
all6 <- all6 %>% select(mlsto, balance.mlsto) %>% distinct()
all6$mlsto <- as.character(all6$mlsto)
all10mice = left_join(all10mice, all6)
head(all10mice)

#merge simp.log
head(new.CR)
all10mice<- cbind(all10mice, new.CR %>% select(simp.log))
all10mice$f.rpdol <- as.factor(all10mice$b.rpdol)
levels(all10mice$f.rpdol)[levels(all10mice$f.rpdol) == "0"] <-"profit"
levels(all10mice$f.rpdol)[levels(all10mice$f.rpdol) == "1"] <-"loss"

#for simp.log 0.6 is the threshold, so summarise everything above 0.6
all10mice %>% filter(simp.log >= 0.6) %>% summary
reject <- all10mice %>% filter(simp.log >= 0.6)
reject$compare <- "reject"

#want to understnad the comparison of perentages between full dataset and rpob>0.6 dataset
all10mice$compare <- "full"
all10mice <- rbind(all10mice, reject)

saveRDS(all10mice, '/Users/yam/OneDrive/shared files/Bligh Tanner/masters/data/reject_plot.rds')

#create % column for factor variable
# count number of cases for each

cols = c(1:11,13,14,18,19,22)

#wot function saves plots to folder in onedrive
wot <- function( compare.cols = compare.cols){

        for (i in seq_along(compare.cols)){
        print(i)

        if(class(all10mice[,compare.cols[i]]) %in% c('numeric','integer')){
                p <- ggplot(all10mice, aes_string(x = names(all10mice)[compare.cols[i]])) + 
                        geom_density() +
                        facet_wrap(~compare)
        }

        if(class(all10mice[,compare.cols[i]]) %in% c('factor')){
                p <- ggplot(all10mice, aes_string(x = names(all10mice)[compare.cols[i]])) + 
                        geom_bar(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..])) +
                        facet_wrap(~compare) + 
                        theme(axis.text.x=element_text(angle=30, hjust=1)) +
                        scale_y_continuous(labels = scales::percent)

        }
                ggsave(p, filename = paste(names(all10mice)[compare.cols[i]], 'compare.png', sep = ""), 
                       path = '/Users/yam/OneDrive/shared files/Bligh Tanner/masters/barplots/compare_simplog/', 
                       width = 5, height = 4)
}}

wot(compare.cols = cols)

#plot of profit size broken up by job
head(reject)

ggplot(reject, aes(x = f.rpdol, y = abs(balance.mlsto), fill = mlsto)) +
        geom_bar(stat = "identity") + 
        theme(legend.position="none") +
        scale_fill_manual(values = rep(c('blue', 'yellow'), 54)) + 
        scale_y_continuous(labels = scales::dollar)
```

groups <- (rbinom(32, n = 5, prob = 0.4))
tapply(groups, groups, sum) #- is almost the same as
table(groups)

ind <- list(c(1, 2, 2), c("A", "A", "B"))
table(ind)
tapply(1:3, ind) #-> the split vector
tapply(1:3, ind, sum)
